---
title: "Lab 11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

1. Tidy the *Project Reads* data
	+ load the Project_Reads_Scores.csv file
	+ Remove columns 5-9
	+ Tidy the remaining dataset such that a case represents a score and percentage within a unit.

```{r q1, echo = FALSE, message = FALSE, warning = FALSE}
library(rio)
library(tidyverse)
library(janitor)
library(here)
theme_set(theme_light())

reads <- import(here("data", "Project_Reads_Scores.csv"), 
                setclass = "tbl_df") %>% 
  clean_names()
View(reads)
names(reads)[18:19] <- c("unit_56_score", "unit_56_percent")

reads_tidy <- reads %>% 
	select(4, 1:3, 10:23) %>% 
	filter(student_id != "All Students (Average)") %>% 
	gather(var, val, contains("unit")) %>% 
	separate(var, c("dis1", "unit", "type"), sep = "_") %>%
	separate(test_year, c("date", "dis2", "dis3"), sep = " ") %>% 
	mutate(date = lubridate::mdy(date)) %>% 
	select(-contains("dis")) %>% 
	spread(type, val, convert = TRUE) %>% 
  mutate(percent = parse_number(percent))

# Alternative date mutate using base
# mutate(date = as.Date(date, format = "%m/%d/%Y")) %>% 
# a little unfair overall, but it's okay if it's not a date

```
2. Produce a summary table of the mean percentage correct for each unit within test sites. Report the summary in a table.

```{r q2, echo = FALSE, eval = FALSE}
reads_summary <- reads_tidy %>% 
	group_by(test_site, unit) %>% 
	summarize(percent = mean(percent))

reads_summary
```

3. Produce a plot of the summary data.

```{r q3, echo = FALSE, eval = FALSE}
ggplot(reads_tidy, aes(unit, percent)) + 
  geom_line(aes(group = student_id), color = "gray80") +
  geom_smooth(aes(group = test_site, color = test_site), lwd = 2, se = FALSE) +
  scale_color_brewer(palette = "Accent")
```

4. Produce at least one more exploratory plot using the tidied data and at least three variables. 

```{r q4, echo = FALSE, eval = FALSE}
ggplot(reads_tidy, aes(unit, score)) +
  geom_bar(stat = "summary", fun.y = "mean", fill = "gray70") +
  geom_jitter(aes(col = test_site), width = 0.25, height = 0) +
  geom_smooth(aes(group = test_site,  color = test_site), se = FALSE) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~test_site) +
  guides(color = "none")
```



