---
title: "Lab 2"
author: "Key"
date: "September 26, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

1. Run the following code to 
  (a) install the {nlme} and {janitor} packages
  (b) load the packages along with the tidyverse, and
  (c) access and quickly prep some data (from the {nmle} package) for plotting.

```{r data-download}
#install.packages(c("nlme", "janitor"))
library(nlme)
library(janitor)
library(tidyverse)
pd <- Oxboys %>% 
  clean_names() %>% 
  mutate(subject = factor(subject),
         occasion = factor(occasion)) %>% 
  filter(subject == "10" | subject == "4" | subject == "7") %>% 
  tbl_df()
```

1. Reproduce the following plots, using the data. You can use whatever theme 
you want, but all else should be the same.

```{r plots1, message = FALSE, warning = FALSE}
theme_set(theme_minimal())

ggplot(pd, aes(age, height)) +
  geom_line() +
  facet_wrap(~subject) +
  ggtitle("Plot 1")

ggplot(pd, aes(age, height, color = subject)) +
  geom_line() +
  ggtitle("Plot 2")
```

\newpage

2. Use the *mtcars* dataset from base R to replicate the following plots.
   (just type *mtcars* into the console to see the dataset).

```{r plots2}
ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  ggtitle("Plot 3")
ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  geom_smooth() +
  ggtitle("Plot 4")
ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~vs) +
  ggtitle("Plot 5")

ggplot(mtcars, aes(drat, mpg, color = factor(cyl))) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Plot 6")
```

\newpage

3. Use the *Orange* dataset, also part of base R, to replicate the following
   plots.
   
```{r orange-plots}
ggplot(Orange, aes(age, circumference, color = Tree)) +
  geom_line() +
  geom_point() +
  ggtitle("Plot 7")
ggplot(Orange, aes(age, circumference)) +
  geom_smooth(method = "lm", se = FALSE, color = "gray40") +
  geom_point(aes(color = Tree), size = 3) +
  labs(x = "Age of the Tree (in days)",
       y = "Circumference of the Trunk (in mm)",
       title = "Orange Tree Growth",
       subtitle = "Gray line displays a linear model fit to the data.")
```
