---
title: "Lab 3"
author: "Your Name Here"
date: "September 26, 2018"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

1. Run the following code to load the *tidyverse*.

```{r load-tidyverse}
library(tidyverse)
```

1. Run the following lines of code to view and read about the data we'll use 
for this lab.

```{r gsscat, eval = FALSE}
str(gss_cat)
View(gss_cat)
?gss_cat
```

2. Use `ggplot` to create a histogram of `tvhours`. The plot should:
  + Include a small amount of transparency so gridlines are visible under the 
    histogram.
  + Be a different color than the default
  + Include meaningful axis labels
  + Have a title and a subtitle

```{r question-2}

```

3. Create a ridgeline density plot of age by `partyid`. Do you notice any strong
  differences by party affiliation?

```{r question-3}
library(ggridges)

```

4. Modify the plot from Question 3 to produce separate densities by `race`. Do 
  you see any patterns?

```{r question-4}

```

5. Replicate the plots from Questions 3 and 4, but this time displaying the 
  relations with boxplots. Which do you think displays the relation more 
  clearly? Why?
  
```{r label, options}

```

6. Run the following lines of code to get a correlation matrix as a data frame.

```{r corr-mat-df}
# install.packages(ISLR)
library(ISLR)
cor_tbl <- Hitters %>% 
  select_if(is.numeric) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  as.data.frame() %>% 
  mutate(row = row.names(.)) %>% 
  gather(col, cor, -row) %>% 
  tbl_df()
```

Use the correlation table to create a heatmap using `geom_tile`. Change the 
colors to one of the four viridis palettes. What does the heatmap help you see?

```{r, heatmap}
ggplot(cor_tbl, aes()) 
```

7. The code below will produce a barplot. 

```{r barplot1}
ggplot(gss_cat, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Use the code below to redefine the `rincome` variable so that *Not applicable*
is displayed first, followed by *No answer*, *Don't know*, *Refused*, and then
each income category from lowest to highest. Once you've redefined the factor
variable, re-produce the plot above. The plot should look as it is below.

```{r redfine-factor, echo = FALSE}
gss_cat <- gss_cat %>% 
  mutate(rincome = factor(rincome, levels = c()))

ggplot(gss_cat, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```