---
title: "Lab 3"
author: "Key"
date: "September 26, 2018"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

1. Run the following code to load the *tidyverse*.

```{r load-tidyverse}
library(tidyverse)
```

1. Run the following lines of code to view and read about the data we'll use 
for this lab.

```{r gsscat, eval = FALSE}
str(gss_cat)
View(gss_cat)
?gss_cat
```

2. Use `ggplot` to create a histogram of `tvhours`. The plot should:
  + Include a small amount of transparency so gridlines are visible under the 
    histogram.
  + Be a different color than the default
  + Include meaningful axis labels
  + Have a title and a subtitle

```{r question-2}
theme_set(theme_minimal())
ggplot(gss_cat, aes(tvhours)) +
  geom_histogram(fill = "cornflowerblue", 
                 alpha = 0.7) +
  labs(x = "Number of Hours Watching Television",
       y = "Number of Observations",
       title = "Distribution of Television Watching",
       subtitle = "Data from the General Social Survey (http://gss.norc.org)")
```

3. Create a ridgeline density plot of age by `partyid`. Do you notice any strong
  differences by party affiliation?

```{r question-3}
library(ggridges)
ggplot(gss_cat, aes(age, partyid)) +
  geom_density_ridges(fill = "cornflowerblue", alpha = 0.4)
```

4. Modify the plot from Question 3 to produce separate densities by `race`. Do 
  you see any patterns?

```{r question-4}
ggplot(gss_cat, aes(age, partyid)) +
  geom_density_ridges(aes(fill = race), alpha = 0.4)
```

5. Replicate the plots from Questions 3 and 4, but this time displaying the 
  relations with boxplots. Which do you think displays the relation more 
  clearly? Why?
  
```{r label, options}
ggplot(gss_cat, aes(partyid, age)) +
  geom_boxplot(fill = "cornflowerblue")

ggplot(gss_cat, aes(partyid, age)) +
  geom_boxplot(aes(fill = race), alpha = 0.4)
```

6. Run the following lines of code to get a correlation matrix as a data frame.

```{r corr-mat-df}
# install.packages(ISLR)
library(ISLR)
cor_tbl <- Hitters %>% 
  select_if(is.numeric) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  as.data.frame() %>% 
  mutate(row = row.names(.)) %>% 
  gather(col, cor, -row) %>% 
  tbl_df()
```

Use the correlation table to create a heatmap using `geom_tile`. Change the 
colors to one of the four viridis palettes. What does the heatmap help you see?

```{r, heatmap}
ggplot(cor_tbl, aes(row, col, fill = cor)) +
  geom_tile() +
  scale_fill_viridis_c(option = "inferno")
```

7. The code below will produce a barplot. 

```{r barplot1}
ggplot(gss_cat, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Use the code below to redefine the `rincome` variable so that *Not applicable*
is displayed first, followed by *No answer*, *Don't know*, *Refused*, and then
each income category from lowest to highest. Once you've redefined the factor
variable, re-produce the plot above. The plot should look as it is below.

```{r redfine-factor, echo = FALSE}
gss_cat <- gss_cat %>% 
  mutate(rincome = factor(rincome, levels = c("Not applicable",
                                              "No answer",
                                              "Don't know",
                                              "Refused",
                                              "Lt $1000",
                                              "$1000 to 2999",
                                              "$3000 to 3999",
                                              "$4000 to 4999",
                                              "$5000 to 5999",
                                              "$6000 to 6999",
                                              "$7000 to 7999",
                                              "$8000 to 9999",
                                              "$10000 - 14999",
                                              "$15000 - 19999",
                                              "$20000 - 24999",
                                              "$25000 or more")))
ggplot(gss_cat, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```