---
title: "Lab 4 Key"
output:
  pdf_document:
    highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = FALSE, 
                      message = FALSE, 
                      warning = FALSE)
```


Install and load the package *Lahman*, which will give you access to the dataset *Teams*

```{r teams_echo, echo = TRUE}
install.packages("Lahman")
library(Lahman)
```
* Produce a subset of the data that has the following characteristics:
    + Only one team (your choice)
    + data from 1980 to present (or as present as the dataset gets)
    + Includes 5 columns: name, yearID, W, L, R, RA

(The variables above correspond to the team name, the year, wins, losses, runs scored, and runs allowed)

* Make sure you select a team that is currently still around, or it probably
won't be interesting (see a list of current at [http://www.espn.com/mlb/teams](http://www.espn.com/mlb/teams)).

* Create a new variable corresponding to the winning percentage for the team 
  you chose over time

$$w_{pct} = \frac{wins}{wins + losses}$$

* Order by winning percentage: Least to greatest
* Order by winning percentage: greatest to least
* Compute the mean and standard deviation of winning percentage
* With the full dataset
  + compute the average and standard deviation of winning percentage for each team. 
  + Order by highest winning percentage
* Use the full data to reproduce the plot below

```{r answers, echo = TRUE}
library(Lahman)
library(tidyverse)

teams <- Teams %>% 
  janitor::clean_names()

cubs <- teams %>% 
    filter(name == "Chicago Cubs" & year_id >= 1980) %>% 
    select(name, year_id, w, l, r, ra)

cubs <- cubs %>% 
    mutate(w_pct = w / (w + l))

cubs %>% 
  arrange(w_pct)

cubs %>% 
  arrange(desc(w_pct))

cubs %>% 
  summarize(mean_winning_pct = mean(w_pct),
            sd_winning_pct = sd(w_pct))

teams %>% 
  mutate(w_pct = w / (w + l)) %>% 
  group_by(name) %>% 
  summarize(n = n(),
            mean_winning_pct = mean(w_pct, na.rm = TRUE),
            sd_winning_pct = sd(w_pct, na.rm = TRUE)) %>% 
  arrange(desc(mean_winning_pct))
```

```{r plot, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
library(Lahman)
library(tidyverse)
teams <- Teams %>% 
  janitor::clean_names()

teams %>% 
  tbl_df() %>% 
  mutate(w_pct = w / (w + l)) %>% 
  filter(name == "New York Yankees" |
         name == "Detroit Tigers" |
         name == "San Diego Padres") %>% 
  ggplot(aes(year_id, w_pct)) + 
    geom_line(aes(color = name)) +
    ggthemes::theme_hc()
```