---
title: "Lab 6"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, eval = FALSE)
```

1. Read in the following three datasets, using {here} and {rio}:
  * *sesame13.sav*
  * *star.csv*
  * *ais.xlsx*
  
*Hint*: For the *ais.xlsx* dataset look at the `skip` argument within the help 
  documentation.
  
```{r import}
library(rio)
sesame <- import(here("data", "sesame13.sav"))
star <- import(here("data", "star.csv"))
ais <- import(here("data", "ais.xlsx"), skip = 15)
```

1. Using the ais data, compute the average red blood cell count and average bmi by sport. Output these data as SPSS and EXCEL files. 

```{r av_rbc}
library(tidyverse)
smry <- ais %>% 
  group_by(sport) %>% 
  summarize(mean_rcc = mean(rcc),
            mean_bmi = mean(bmi))
export(smry, "summary_measures.sav")
export(smry, "summary_measures.xlsx")
```

1. Use the sesame dataset to answer the following question: Was the average 
  female age higher in schools or at home? 

```{r av_age}
sesame %>% 
  characterize() %>% 
  filter(sex == "Female") %>% 
  group_by(setting) %>% 
  summarize(mean_age = mean(age))
# Answer: School
```

1. How many rows and columns are in the *star* dataset? Remove outliers using a really poor method, just for practice, by eliminating students whose math (*tmathss*) scores were more than three standard deviations above or below the corresponding mean. How many rows are in the dataset now?

```{r rem_outlier}
dim(star) # 5748 rows, 12 columns
star %>% 
  filter(tmathss <= mean(tmathss) + 3*sd(tmathss) &
         tmathss >= mean(tmathss) - 3*sd(tmathss)) %>% 
  nrow()
# Answer: 5743  
```

1. Use the star dataset to compute standardized versions of the math and reading scores, i.e., for each variable, subtract the mean from each observation and divide by the standard deviation: $x_s = \frac{x_i - \bar{X}}{sd(X)}$. 
  + Check that your computations were correct by computing the mean and standard deviation of each variable (they should be 0 and 1). 
  + Compute the mean of the standardized variable for all sex/frl combinations (I'm asking you to extend what you know, we haven't talked explicitly about how to do this yet). 
  + What do you make of these findings? Do you see a gender effect? FRL effect? Is there evidence of an interaction? (i.e., that the effect of FRL is greater for boys versus girls). 

```{r q6}
star <- star %>% 
  mutate(stand_math = (tmathss - mean(tmathss)) / sd(tmathss),
         stand_rdg  = (treadss - mean(treadss)) / sd(treadss))

star %>% 
  summarize(stand_math_mean = mean(stand_math),
            stand_math_sd   = sd(stand_math),
            stand_rdg_mean = mean(stand_rdg),
            stand_rdg_sd   = sd(stand_rdg))

star %>% 
  group_by(sex, frl) %>% 
  summarize(stand_math_mean = mean(stand_math),
            stand_math_sd   = sd(stand_math),
            stand_rdg_mean = mean(stand_rdg),
            stand_rdg_sd   = sd(stand_rdg))
```
