---
title: "Lab 6 Key"
author: "Daniel Anderson"
output:
  html_document:
    highlight: pygments
  pdf_document:
    highlight: kate
---


1. Create a new R Markdown document and modify the YAML to 
  + Include your name
  + Change the syntax highlighting to any scheme but the default. The options
    are `default`, `tango`, `pygments`, `kate`, `monochrome`, `espresso`,
    `zenburn`, `haddock`, and `textmate`. You can also use `NULL` if you want 
    no highlighting.
  + Include the option to make it easy to modify the rendering between PDF and
    HTML.
  

2. Create a code chunk that
  + Does not display the code or any warnings, messages, etc. from the code, 
    but evaluates every function/line of the code.
  + Loads all the packages you decide to use for the lab
  + Sets a global chunk option to make all figures 6.5" wide and the height to
    a value that makes sense to you.

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5,
                      fig.height = 4)
library(rio)
library(here)
library(tidyverse)
library(janitor)

theme_set(theme_minimal(base_size = 8))
```

3. Load the *ecls-k_samp.sav* dataset, and produce the plot below. Do not show
   the code you used (colors, themes, etc. don't matter here).

```{r load-data}
d <- import(here("data", "ecls-k_samp.sav"),
            setclass = "tbl_df") %>%
        characterize() %>%
        clean_names() 

d %>% 
  count(ethnic)

d %>%
  filter(ethnic == "WHITE, NON-HISPANIC" |
         ethnic == "BLACK OR AFRICAN AMERICAN, NON-HISPANIC" |
         ethnic == "HISPANIC, RACE SPECIFIED" |
         ethnic == "HISPANIC, RACE NOT SPECIFIED") %>%
ggplot(aes(t1mscale, t2mscale)) +
  geom_point() +
  geom_smooth(aes(color = school_type),
              method = "lm") +
  facet_wrap(~ethnic)
```

\newpage

4. Run The following lines of code to store the mean and standard deviation of
  `t1mscale`. Extend this code to calculate (in the same code chunk) the mean
  and standard deviation of `t2mscale`. Note this code assumes you read the 
  ecls-k dataset in as an object called `d`. You should substitute in whatever 
  the name is for your data object. 


```{r means-sd, echo = TRUE}
t1mean <- mean(d$t1mscale, na.rm = TRUE)
t1sd <- sd(d$t1mscale, na.rm = TRUE)

t2mean <- mean(d$t2mscale, na.rm = TRUE)
t2sd <- sd(d$t2mscale, na.rm = TRUE)
```

Using the values you calculated above, use an inline code evaluation to report
the means/sds for the two time points. Also report the difference between the
means (i.e., the average gain).

----

The mean for time point one was `r round(t1mean, 2)`, with a standard deviation of `r round(t1sd, 2)`. At time point two, the mean was `r round(t2mean, 2)`, with a standard deviation of `r round(t2sd, 2)`. The difference between the means was between the time points was thus `r abs(round(t2mean - t1mean, 2))` points.

----

5. Pretend you are trying to teach somebody how to load data. Describe the
   process below that we've discussed in class, including why it helps 
   reproducibility, and echo chunks of code as necessary without actually
   evaluating any of it.


---

Create and RStudio project. This will serve as the root directory. Create empty *data* and *scripts* folders. Place any data you have in the data folder. 

To import the data, create a new script, then load the following packages

```{r load-tutorial, eval = FALSE}
library(rio)
library(here)
```

If you don't have these packages installed, you'll need to install them first, using  `install.packages(c("rio", "here"))`.

Finally, use the {here} library to navigate file paths, and `rio::import` to import data of basically any type. For example, assuming you have created an RStudio project and you are working from that project, and you've put the data you want to load in at folder called *data*, any of the following should work

```{r import-data, eval = FALSE}
d <- import(here("data", "data_to_load.sav"),
            setclass = "tbl_df")

d <- import(here("data", "data_to_load.xlsx"),
            setclass = "tbl_df")

d <- import(here("data", "data_to_load.dta"),
            setclass = "tbl_df")
```

Note that the `setclass` argument is optional, and changes the import to a tibble instead of a standard data frame.