---
title: "Lab 9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

1. Create a new APA R Markdown document. Modify the YAML so 
  + the odd spacing around paragraphs and headers is removed
  + Equations are left-aligned
2. Modify the YAML so a table of contents is included, including headers up to four levels.
  + Include some example text in the document with at least four levels of headers.
  + Include some text that is bold and some that is italics.
3. Write the code to load the ecls-k data. Do not show the code in the document.
4. The following displays a regression model. Reproduce the equation somewhere
in your document

$$
math_{t2_i} = \alpha + \beta_1(math_{t1_i}) + \beta_2(SES_{cat_i}) + \beta_3(math_{t1_i} \times SES_{cat_i}) \epsilon
$$

5. Reproduce the following plot in your document. (Note, this is a visual display of the model above)

```{r answers, echo = FALSE, warning = FALSE, message = FALSE}
library(rio)
library(tidyverse)
library(here)

d <- import(here("data", "ecls-k_samp.sav"),
            setclass = "tbl_df") %>% 
  characterize() %>% 
  janitor::clean_names() %>% 
  mutate(ses_cat = factor(ses_cat, 
                          levels = c("FIRST QUINTILE",
                                     "SECOND QUINTILE",
                                     "THIRD QUINTILE",
                                     "FOURTH QUINTILE",
                                     "FIFTH QUINTILE"),
                          labels = c("First",
                                     "Second", 
                                     "Third", 
                                     "Fourth", 
                                     "Fifth")))
  

ggplot(d, aes(t1mscale, t2mscale))  +
  geom_point(color = "gray70") +
  geom_smooth(aes(color = ses_cat),
              method = "lm",
              se = FALSE) +
  scale_color_viridis_d("SES Quintile") +
  labs(title = "Math scores",
       subtitle = "Relation from Time 1 to Time 2",
       x = "Math Score (time 1)",
       y = "Math Score (time 2)") +
  theme_minimal()
```



